---
title: "`r paste('Silverlake Bank', Sys.getenv('BANKNUM'), 'Exceptions')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r global, include=FALSE}
library(dplyr)
library(tidyr)
library(purrr)
library(DBI)
library(flexdashboard)
library(shiny)
library(DT)
library(RJDBC)

datatable2 <- function(x, vars = NULL, opts = NULL, ...) {
  
  names_x <- names(x)
  if (is.null(vars)) stop("'vars' must be specified!")
  pos <- match(vars, names_x)
  if (any(map_chr(x[, pos], typeof) == "list"))
    stop("list columns are not supported in datatable2()")
  
  pos <- pos[pos <= ncol(x)] + 1
  rownames(x) <- NULL
  if (nrow(x) > 0) x <- cbind(' ' = '&#10133;', x)

  # options
  opts <- c(
    opts, 
    list(
      columnDefs = list(
        list(visible = FALSE, targets = c(0, pos)),
        list(orderable = FALSE, className = 'details-control', targets = 1),
        list(className = 'dt-left', targets = 1:3),
        list(className = 'dt-right', targets = 4:ncol(x))
      )
  ))
  
  datatable(
    x, 
    ...,
    escape = -2,
    options = opts,
    callback = JS(.callback2(x = x, pos = c(0, pos)))
  )
}

.callback2 <- function(x, pos = NULL) {
  
  part1 <- "table.column(1).nodes().to$().css({cursor: 'pointer'});"
  
  part2 <- glue::glue("
                      var format = function(d) {{
                         text = '<div><table >' +
                                   '<thead>' +
                                      '<tr>' +
                                          '<th></th>' +
                                          '<th>' + 'Example 1' + '</th>' +
                                          '<th>' + 'Example 2' + '</th>' +
                                      '</tr>' +
                                   '</thead>' +
                                      '<tr>' +
                                          '<td>' + 'Customer' + '</td>' +
                                          '<td>' + d[{pos[2]}] + '</td>' +
                                          '<td>' + d[{pos[3]}] + '</td>' +
                                      '</tr>' +
                                      '<tr>' +
                                          '<td>' + 'SL Account' + '</td>' +
                                          '<td>' + d[{pos[4]}] + '</td>' +
                                          '<td>' + d[{pos[5]}] + '</td>' +
                                      '</tr>' +
                                      '<tr>' + 
                                          '<td>' + 'SL Value' + '</td>' +
                                          '<td>' + d[{pos[6]}] + '</td>' +
                                          '<td>' + d[{pos[7]}] + '</td>' +
                                      '</tr>' +
                                      '<tr>' +
                                          '<td>' + 'Old Account' + '</td>' +
                                          '<td>' + d[{pos[8]}] + '</td>' +
                                          '<td>' + d[{pos[9]}] + '</td>' +
                                      '</tr>' +
                                      '<tr>' + 
                                          '<td>' + 'Old Value' + '</td>' +
                                          '<td>' + d[{pos[10]}] + '</td>' +
                                          '<td>' + d[{pos[11]}] + '</td>' +
                                      '</tr>' +
                                      '</table></div>' +
                                      '<b>' + 'Issue Notes' + '</b>' + 
                                      '<p>' + d[{pos[12]}] +
                                              d[{pos[13]}] +
                                              d[{pos[14]}] +
                                              d[{pos[15]}] +
                                              d[{pos[16]}] +
                                              d[{pos[17]}] +
                                              d[{pos[18]}] +
                                              d[{pos[19]}] +
                                      '</p>' +
                                      '<b>' + 'Problem Notes from Jack Henry' + '</b>' +
                                      '<p>' + d[{pos[20]}] + '</p>'
                         return text;}};")
  
  part3 <- 
  "
   table.on('click', 'td.details-control', function() {
    var td = $(this), row = table.row(td.closest('tr'));
    if (row.child.isShown()) {
      row.child.hide();
      td.html('&#10133;');
    } else {
      row.child(format(row.data())).show();
      td.html('&#10134;');
    }
  });"
  
  paste(part1, part2, part3)
} 

.child_row_table2 <- function(x, pos = NULL) {
  
  names_x <- paste0(names(x), ":")
  text <- "
  var format = function(d) {
    text = '<div><table >' + 
  "

  for (i in seq_along(pos)) {
    text <- paste(text, glue::glue(
        "'<tr>' +
          '<td>' + '{names_x[pos[i]]}' + '</td>' +
          '<td>' + d[{pos[i]}] + '</td>' +
        '</tr>' + " ))
  }

  paste0(text,
    "'</table></div>'
      return text;};"
  )
}

get_trip_data <- function() {
   db <- as.list(Sys.getenv(c("AS400HOST", "AS400LIB", "AS400USER", "AS400PWD"), names = T))
   
   con_string <- paste0("jdbc:as400://", db$AS400HOST,"/",db$AS400LIB,";prompt=false;access=read only")
   
   core <- DBI::dbConnect(RJDBC::JDBC(driverClass = "com.ibm.as400.access.AS400JDBCDriver",classPath = "jt400.jar"),
                            con_string,
                            user = db$AS400USER,
                            password = db$AS400PWD,
                            readonly = TRUE)
   
   trips <- dbGetQuery(core, "SELECT TRIPNUM, MAX(DATE('20' || SUBSTR(FILEDATE, CHARACTER_LENGTH(FILEDATE)-1, 2) || '-' || RTRIM(SUBSTR(FILEDATE, CHARACTER_LENGTH(FILEDATE)-5, 2)) || '-' || SUBSTR(FILEDATE, CHARACTER_LENGTH(FILEDATE)-3, 2) )) AS FILE_DATE FROM EXCEPT GROUP BY TRIPNUM ORDER BY FILE_DATE DESC") %>% pull(TRIPNUM)
   
   dbDisconnect(core)
   
   default_env <- Sys.getenv("DEFAULT_TRIP")
   
   if(default_env == "") {
     default <- first(trips)
   } else {
     default <- default_env
   }
   
   list(trips = trips,
        default = default)
}
```

```{r functions}
all_query_data <- reactive({
   #invalidateLater(300000)
   db <- as.list(Sys.getenv(c("AS400HOST", "AS400LIB", "AS400USER", "AS400PWD"), names = T))
   
   con_string <- paste0("jdbc:as400://", db$AS400HOST,"/",db$AS400LIB,";prompt=false;access=read only")
   
   core <- DBI::dbConnect(RJDBC::JDBC(driverClass = "com.ibm.as400.access.AS400JDBCDriver",classPath = "jt400.jar"),
                            con_string,
                            user = db$AS400USER,
                            password = db$AS400PWD,
                            readonly = TRUE)
   all_data <- dbGetQuery(core, "SELECT TRIPNUM, APPPRFX, APPNAME, APPNUM, FDESC1, FDESC2, VERTEAM, PROBLEM, RESOLVED, APPROVED,
                                 CURRENT_TIMESTAMP AS DATA_REFRESH, CUST1, CUST2, OLDACC1, OLDACC2, JHAACC1, JHAACC2, OLDVAL1,
                                 OLDVAL2, JHAVAL1, JHAVAL2, ISSUE1, ISSUE2, ISSUE3, ISSUE4, ISSUE5, ISSUE6, ISSUE7, ISSUE8, PROBLEM1
                          FROM EXCEPT") %>%
    mutate(DATA_REFRESH = as.POSIXct(DATA_REFRESH, tz = Sys.getenv("TZ")))
   dbDisconnect(core)
   return(all_data)
   })



all_date_time <- reactive({
   all_query_data()$DATA_REFRESH[1]
})


current_test <- reactive({
      all_query_data() %>%
      filter(TRIPNUM == input$test, APPROVED != "I") %>%
      unite(col = "DESC", FDESC1, FDESC2, sep = " ") %>%
      mutate(APPNAME = trimws(APPNAME),
             APPNUM = as.integer(APPNUM),
             VERTEAM = trimws(VERTEAM),
             DESC = trimws(DESC))
})

cif_dep <- reactive({
   current_test() %>%
   filter(APPPRFX %in% c("CD", "CF", "DD", "IR", "SV", "SD"))
})

ln <- reactive({
   current_test() %>%
   filter(APPPRFX %in% c("LN"))
})

gl <- reactive({
   current_test() %>%
   filter(APPPRFX %in% c("AP", "GL"))
})

open_ex_box <- function(df) {
   df %>% 
      filter(RESOLVED != 'R', PROBLEM != 'N',
             !(APPROVED %in% c("C", "R"))) %>%
      tally() %>%
      pull() %>%
      as.integer() %>%
      valueBox(color = "red", icon = "fa-exclamation") %>%
      return()
}

pending_ex_box <- function(df) {
   df %>%
      filter(RESOLVED == 'R' | PROBLEM == 'N',
             !(APPROVED %in% c("C", "R"))) %>%
      tally() %>%
      pull() %>%
      as.integer() %>%
      valueBox(color = "orange", icon = "fa-search") %>%
      return()
}

resolved_ex_box <- function(df) {
   df %>%
      filter(APPROVED %in% c("C", "R")) %>%
      tally() %>%
      pull() %>%
      as.integer() %>%
      valueBox(color = "green", icon = "fa-check") %>%
      return()
}

exception_view <- function(df) {
  df %>%
    select(APPNAME, APPNUM, DESC, VERTEAM, P = PROBLEM, R = RESOLVED, A = APPROVED,
             CUST1, CUST2, OLDACC1, OLDACC2, JHAACC1, JHAACC2, OLDVAL1, OLDVAL2, JHAVAL1, JHAVAL2,
             ISSUE1, ISSUE2, ISSUE3, ISSUE4, ISSUE5, ISSUE6, ISSUE7, ISSUE8, PROBLEM1) %>%
      arrange(APPNAME, APPNUM) %>%
      datatable2(vars = c("CUST1", "CUST2",
                          "JHAACC1", "JHAACC2",
                          "JHAVAL1", "JHAVAL2",
                          "OLDACC1", "OLDACC2",
                          "OLDVAL1", "OLDVAL2",
                          "ISSUE1", "ISSUE2", "ISSUE3", "ISSUE4", "ISSUE5", "ISSUE6", "ISSUE7", "ISSUE8",
                          "PROBLEM1"),
                 opts = list(
                   paging = FALSE,
                   scrollY = '77vh'
                  )
                 ) %>%
      return()
}

list_open_exceptions <- function(df) {
   df %>%
      filter(RESOLVED != 'R', PROBLEM != 'N',
             !(APPROVED %in% c("C", "R"))) %>%
      exception_view() %>%
      return()
}

list_pending_exceptions <- function(df) {
   df %>%
      filter(RESOLVED == 'R' | PROBLEM == 'N', 
             !(APPROVED %in% c("C", "R"))) %>%
      exception_view() %>%
      return()
}

list_resolved_execptions <- function(df) {
   df %>%
      filter(APPROVED %in% c("C", "R")) %>%
      exception_view() %>%
      return()
}

```

Bank Wide
=======================================================================

Column {data-width=150} 
-----------------------------------------------------------------------

### Open Exceptions

```{r}
renderValueBox(open_ex_box(current_test()))
```

### Pending Validation

```{r}
renderValueBox(pending_ex_box(current_test()))
```

### Closed Exceptions

```{r}
renderValueBox(resolved_ex_box(current_test()))
```

### Test Number: {data-height=55}

```{r}
renderText(input$test)
```

### Last Refresh:

```{r}
renderText(format(all_date_time(), "%m/%d/%Y %H:%M:%S"))
```

Column {.tabset data-width=850}
------------------------------------------------------------------------

### Open

```{r}
renderDT(list_open_exceptions(current_test()))
```

### Pending Validation

```{r}
renderDT(list_pending_exceptions(current_test()))
```

### Closed

```{r}
renderDT(list_resolved_execptions(current_test()))
```


CIF/Deposit
========================================================================

Column {data-width=150} 
-----------------------------------------------------------------------

### Open Exceptions

```{r}
renderValueBox(open_ex_box(cif_dep()))
```

### Pending Validation

```{r}
renderValueBox(pending_ex_box(cif_dep()))
```

### Closed Exceptions

```{r}
renderValueBox(resolved_ex_box(cif_dep()))
```

### Test Number: {data-height=55}

```{r}
renderText(input$test)
```

### Last Refresh:

```{r}
renderText(format(all_date_time(), "%m/%d/%Y %H:%M:%S"))
```

Column {.tabset data-width=850}
------------------------------------------------------------------------

### Open

```{r}
renderDT(list_open_exceptions(cif_dep()))
```

### Pending Validation

```{r}
renderDT(list_pending_exceptions(cif_dep()))
```

### Closed

```{r}
renderDT(list_resolved_execptions(cif_dep()))
```


Loans
========================================================================

Column {data-width=150} 
-----------------------------------------------------------------------

### Open Exceptions

```{r}
renderValueBox(open_ex_box(ln()))
```

### Pending Validation

```{r}
renderValueBox(pending_ex_box(ln()))
```

### Closed Exceptions

```{r}
renderValueBox(resolved_ex_box(ln()))
```

### Test Number: {data-height=55}

```{r}
renderText(input$test)
```

### Last Refresh:

```{r}
renderText(format(all_date_time(), "%m/%d/%Y %H:%M:%S"))
```


Column {.tabset data-width=850}
------------------------------------------------------------------------

### Open

```{r}
renderDT(list_open_exceptions(ln()))
```

### Pending Validation

```{r}
renderDT(list_pending_exceptions(ln()))
```

### Closed

```{r}
renderDT(list_resolved_execptions(ln()))
```


GL
=========================================================================

Column {data-width=150} 
-----------------------------------------------------------------------

### Open Exceptions

```{r}
renderValueBox(open_ex_box(gl()))
```

### Pending Validation

```{r}
renderValueBox(pending_ex_box(gl()))
```

### Closed Exceptions

```{r}
renderValueBox(resolved_ex_box(gl()))
```

### Test Number: {data-height=55}

```{r}
renderText(input$test)
```

### Last Refresh:

```{r}
renderText(format(all_date_time(), "%m/%d/%Y %H:%M:%S"))
```


Column {.tabset data-width=850} 
------------------------------------------------------------------------

### Open

```{r}
renderDT(list_open_exceptions(gl()))
```

### Pending Validation

```{r}
renderDT(list_pending_exceptions(gl()))
```

### Closed

```{r}
renderDT(list_resolved_execptions(gl()))
```

Lookup Exception
========================================================================

Column {data-width=150}
------------------------------------------------------------------------

```{r}
fillCol(width = 150, flex = c(NA, NA),
    textInput("appname", "APPNAME:", value = ""),
    textInput("appnum", "APPNUM:", value = "")
)
```

Column {data-width=900}
-------------------------------------------------------------------------

### Status {data-height=50}

```{r}
renderValueBox({
    if(input$appname == "" | input$appnum == "") {
        return(valueBox(value = ""))
    }
    
    ticket <- current_test() %>%
      filter(APPNAME == toupper(input$appname), APPNUM == as.numeric(input$appnum)) %>%
        mutate(STATUS = case_when(PROBLEM == 'N' ~ "Non-Issue",
                                 APPROVED %in% c("C", "R") ~ "Closed",
                                 RESOLVED == 'R' ~ "Pending Validation",
                                 TRUE ~ "Open"),
               COLOR = case_when(PROBLEM == 'N' ~ "blue",
                                 APPROVED %in% c("C", "R") ~ "green",
                                 RESOLVED == 'R' ~ "orange",
                                 TRUE ~ "red"),
               ICON = case_when(PROBLEM == 'N' ~ "fa-ban",
                                 APPROVED %in% c("C", "R") ~ "fa-check",
                                 RESOLVED == 'R' ~ "fa-search",
                                 TRUE ~ "fa-exclamation")) %>%
       select(STATUS, COLOR, ICON)
    
    valueBox(value = ticket$STATUS, caption = NULL, color = ticket$COLOR, icon = ticket$ICON, href = NULL)
})
```


### Summary {data-height=150}

```{r}
renderTable({
    if(input$appname == "" | input$appnum == "") {
        return()
    }
    
    current_test() %>%
      filter(APPNAME == toupper(input$appname), APPNUM == as.numeric(input$appnum)) %>%
        select(APPNAME, APPNUM, DESC, VERTEAM, P = PROBLEM, R = RESOLVED, A = APPROVED)
})
```


### Examples {data-height=300}

```{r}
renderTable({
    if(input$appname == "" | input$appnum == "") {
        return()
    }
    
    current_test() %>%
      filter(APPNAME == toupper(input$appname), APPNUM == as.numeric(input$appnum)) %>%
      select(CUST1, CUST2, OLDACC1, OLDACC2, JHAACC1, JHAACC2, OLDVAL1, OLDVAL2, JHAVAL1, JHAVAL2) %>%
      gather(key = "VARIABLE",value = "VALUE", everything()) %>%
      mutate(EXAMPLE = case_when(grepl("1$", VARIABLE) ~ "EXAMPLE_1",
                              grepl("2$", VARIABLE) ~ "EXAMPLE_2"),
          VARIABLE = gsub("[[:digit:]]$", "", VARIABLE)) %>%
      spread(EXAMPLE, VALUE)
})
```

### Issue Notes {data-height=300}

```{r}
renderText({
    if(input$appname == "" | input$appnum == "") {
        return()
    }
    
    current_test() %>%
      filter(APPNAME == toupper(input$appname), APPNUM == as.numeric(input$appnum)) %>%
      select(starts_with("ISSUE")) %>%
      gather(key = "LINE", value = "ISSUE_NOTES", everything()) %>%
      pull(ISSUE_NOTES)
})
```


### Problem Notes from Jack Henry {data-height=300}

```{r}
renderText({
    if(input$appname == "" | input$appnum == "") {
        return()
    }
    
    current_test() %>%
      filter(APPNAME == toupper(input$appname), APPNUM == as.numeric(input$appnum)) %>%
      select(starts_with("PROBLEM")) %>%
      gather(key = "LINE", value = "PROBLEM_NOTES", everything()) %>%
      pull(PROBLEM_NOTES)
})
```

Test Selection
========================================================================

```{r inputs}
   selectInput("test",
      label = "Test Number:",
      choices = get_trip_data()$trips,
      selected = get_trip_data()$default,
      multiple = F)
```